Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-17 chi2012.tex
delicious excel

\subsection{Condition B (control)}
In the B conditions, participants were given the option of using websites and or a spreadsheet to make their choice.  Participants who opted to use websites to make their decisions repeatedly encountered a number of difficulties and issues. In particular, there was significant confusion over the meaning of data points, for example the percentage-based rankings of university teaching by the Times Higher Education. There were numerous usability issues in using websites, particularly in searching for university courses and course requirements. Similarly, participants found it difficult to understand the locations of restaurants in cities that they were not familiar, and could not find a way to plot the shortlist of restaurants onto the same map using the websites. Overall, the users that spent the most time using websites exhibited significant frustration attempting to locate and compare different criteria (such as course entry requirements, or restaurant locations), and all ended up falling back to using the supplied spreadsheets.

@@

>>>>

\subsection{Condition B: Observations and Issues (Websites + Excel)}
In the B conditions, participants were given the option of using websites and or a spreadsheet to make their choice.  For B trials, we measured the fraction of the trial time spent in Excel versus looking at the sites in a 5-value range (0,25,50,75,100\%).  Six individuals used Excel entirely without consulting the web sites at all, while one avoided Excel altogether; most fell somewhere in between, with a median use of 75\% Excel.   When asked to explain their choice post-hoc, participants who used Excel explained that it saved them the effort of having to individually seach and consolidate information from the websites (10 participants).  Participants who looked at websites chose to do so when they needed to know more than what was provided in the spreadsheets (8 participants), when they mistrusted the information in them (1 participant), or if they were not familiar with Excel (1 participant).

Of the Excel use, most participants made minor formatting and column sizing changes to facilitate reading and interpreting the spreadsheets, while four made extensive edits to the sheets to help them ``think through'' the task in various ways.  These uses of Excel for external cognition varied from merely copying over candidate choices from one sheet to the next, sorting values by multiple columns (which participants had considerable trouble with), and colour-coding cells to allow easy counting of  ``pros'' and ``cons''; ``I can't deal with so many textual values; I need colours to help me see'' (p6).

@@

Participants who used websites to make their decisions often encountered several difficulties and issues. In particular, there was significant confusion over the meaning of data points, for example the percentage-based rankings of university teaching by the Times Higher Education. There were numerous usability issues in using websites, particularly in searching for university courses and course requirements. Similarly, participants found it difficult to understand the locations of restaurants in cities that they were not familiar, and could not find a way to plot the shortlist of restaurants onto the same map using the websites. Overall, the users that spent the most time using websites exhibited significant frustration attempting to locate and compare different criteria (such as course entry requirements, or restaurant locations), and all ended up falling back to using the supplied spreadsheets.
